### 2016-06-20 store-consistency.tex
Edits.

\paragraph{A CC store} A causally consistent data store, such as the
one underlying the reasoning framework of~\cite{gotsmanpopl16}, allows
operations to only witness a causally consistent snapshot of the
global state. A straightforward trace invariant ($\I_s$) for this
store is the \C{CC} guarantee that requires an effect to witness all
causally preceding effects regardless of the isolation requirements of
its transaction:
\begin{smathpar}
\begin{array}{lccl}
\C{CC}(\E) & \;=\; &  & \forall \eta_1,\eta_2.\, 
      \E \Vdash \eta_1 \soar \eta_2 \Rightarrow  \underE{\eta_1 \visar
      \eta_2}\\
    &   & \wedge & \forall\eta_1,\eta_2,\eta_3.\,\underE{\eta_1 \visar
      \eta_2} \conj \underE{\eta_2 \visoar \eta_3} \\
    &   & &\hspace*{0.5in} \Rightarrow \underE{\eta_1 \visar \eta_3}\\
\end{array}
\end{smathpar}
However, like $\I_s = \C{SC}$, $\I_s = \C{CC}$ may induce the store to
meet isolation requirements by restricting concurrency, thus failing
to abide by the spirit of weak isolation. In order to admit weak
isolation without restricting concurrency, we weaken $\I_s$ while
being guided by the maximum visibility principle. The weakened $\I_s$
is shown below:
\begin{smathpar}
\begin{array}{lccl}
\C{CC}(\E) & \;=\; &  & \forall \eta_1,\eta_2.\, 
      \E \Vdash \eta_1 \soar \eta_2 \Rightarrow  \underE{\eta_1 \visar
      \eta_2} \\
    & & & \hspace*{0.6in}\disj \neg\I_c(\E \cup 
                (\emptyset,\{(\eta_1,\eta_2)\}))\\
    &   & \wedge & \forall\eta_1,\eta_2,\eta_3.\,\underE{\eta_1 \visar
      \eta_2} \conj \underE{\eta_2 \visoar \eta_3} \\
    &   & &\hspace*{0.3in} \Rightarrow \underE{\eta_1 \visar \eta_3}
      \disj \neg\I_c(\E \cup (\emptyset,\{(\eta_1,\eta_2)\}))\\
\end{array}
\end{smathpar}
Instantiating the parameter $\I$  with $\I_s \wedge \I_c$ results in
an operational semantics that admits the violation of causal
consistency if and only if the violation is inevitable to enforce
$\I_c$.

>>>>

\paragraph{A CC store} A causally consistent data store, such as the
one underlying the reasoning framework of~\cite{gotsmanpopl16}, allows
operations to only witness a causally consistent snapshot of the
global state. A straightforward trace invariant ($\I_s$) for this
store is the \C{CC} guarantee that requires an effect to witness all
causally preceding effects regardless of the isolation requirements of
its transaction:
\begin{smathpar}
\begin{array}{lccl}
\C{CC}(\E) & \;=\; &  & \forall \eta_1,\eta_2.\, 
      \E \Vdash \eta_1 \soar \eta_2 \Rightarrow  \underE{\eta_1 \visar
      \eta_2}\\
    &   & \wedge & \forall\eta_1,\eta_2,\eta_3.\,\underE{\eta_1 \visar
      \eta_2} \conj \underE{\eta_2 \visoar \eta_3} \\
    &   & &\hspace*{0.5in} \Rightarrow \underE{\eta_1 \visar \eta_3}\\
\end{array}
\end{smathpar}
However, like $\I_s = \C{SC}$, $\I_s = \C{CC}$ may induce the store to
meet isolation requirements by restricting concurrency, thus failing
to abide by the spirit of weak isolation. In order to admit weak
isolation without restricting concurrency, we weaken $\I_s$ while
being guided by the maximum visibility principle. The weakened $\I_s$
is shown below:
\begin{smathpar}
\begin{array}{lccl}
\C{CC}(\E) & \;=\; &  & \forall \eta_1,\eta_2.\, 
      \E \Vdash \eta_1 \soar \eta_2 \Rightarrow  \underE{\eta_1 \visar
      \eta_2} \\
    & & & \hspace*{0.6in}\disj \neg\I_c(\E \cup 
                (\emptyset,\{(\eta_1,\eta_2)\}))\\
    &   & \wedge & \forall\eta_1,\eta_2,\eta_3.\,\underE{\eta_1 \visar
      \eta_2} \conj \underE{\eta_2 \visoar \eta_3} \\
    &   & &\hspace*{0.3in} \Rightarrow \underE{\eta_1 \visar \eta_3}
      \disj \neg\I_c(\E \cup (\emptyset,\{(\eta_1,\eta_2)\}))\\
\end{array}
\end{smathpar}
Instantiating the parameter $\I$  with $\I_s \wedge \I_c$ in
Fig.~\ref{fig:txnimp} results in an operational semantics that admits
the violation of causal consistency if and only if the violation is
inevitable to enforce
$\I_c$.
